Interpolation and extrapolation based performance measurement of Analytical and Artificial Neural Network models in predicting hot deformation behavior of a medium carbon steel

### 2023-01-11 Article.tex
Restore Correct versions of Article

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage[colorlinks = true]{hyperref}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
The manufacturing of large size forged blocks made of high-strength steels (as medium carbon alloy steel) is a process whose first step is ingot casting, followed by forging, quenching, and tempering operations. These forged blocks are used in automative industry  as die materials for the production of plastic injection components \cite{chadha2017deformation,chadha2018influence,murugesan2019two, murugesan2019hybrid}. For more industrial applications, requirements such as chemical homogeneity, uniform hardness and grain size inside these large size forged blocks are importants. The ingot breakdown which is the first step of the deformation process, is carried out generally to get the above requirements and strengthening or weakening of alloy may result. Work hardening (WH), phase transformation, and precipitation are those that often have strengthening effects while dynamic recovery (DRV), metadynamic recristallization (MDRX), dynamic recristallization (DRX), static recovery and static recristallization occur in the material softening. Strengthening or weakening effects strongly depends on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$ and impact the mechanical properties of the final product \cite{tavakoli2019ferrite, ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}. As conducting an experiment is very expensive and time consuming, numerical simulation such as the Finite Element Analysis (FEA), where a good result depends on the behavior laws of the materials, is widely used nowadays to reduce experimental errors \cite{Mandal-2009, Qin-2010, Ji-2018,Lin-2008-P, Wu-2012}.

To predict the flow stress behavior during the breakdown process of ingots, many constitutive models have been proposed to simulate the thermomechanical process among which, phenomenological, semi-empirical, physical models or models based on Artificial Neural Networks (ANN) \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021}. Among the large number of models available in the literature, the Johnson-Cook (JC) \cite{Johnson-1983} and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes. The JC model is the most widely used because it is simple to identify and use and has few parameters to determine \cite{NematNasser-2003, Khan-2004}. However, this model, in its original state, has some shortcomings due to non-coupling effect of strain, strain rate and temperature as analyzed by Jia \eal \cite{Jia-2021}. To circumvent these shortcomings, several modified forms of the JC model have been developed \cite{Rule-1998, Vural-2003, Lin-2010, Lin-2012, Li-2013, Zhang-2015, Zhou-2019}.
Due to its more physics-based formulation, the ZA model is often preferred to the JC model because it allows the coupling of strain rate and temperature effects \cite{Johnson-1988, Voyiadjis-2005, Dey-2007}.
However, this model has other drawbacks related to the limit value of the test temperature. Indeed, this model applies only to low strain rates and for temperatures limited to about 60~\% of $T_m$ (where $T_m$ is the melting temperature of the material) \cite{Chiou-2005, Lee-2005, Lee-2006, Chen-2007}.
Moreover, the ZA model, in its original form, does not take into account the coupling between deformation and temperature effects \cite{Samantaray-2009}.
In order to reduce these shortcomings (and to apply this model to a wider range of temperatures) of the ZA model, modified forms of Zerilli-Armstrong (MZA) have been proposed \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021}. The Arrhenius-type hyperbolic sine constitutive model is one of the most widely used phenomenological models both for the prediction of the hot deformation behavior of materials and for the analysis of the micro-structure of the material under study because this model allows the estimation of the activation energy for deformation \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}.
Its original formulation has been revised several times for a more accurate description of the high temperature deformation behavior. In order to increase the accuracy of the model, the effects of strain \cite{Slooff-2007, Li-2012, Xu-2013}, strain rate \cite{Lin-2008-C, Mandal-2009} have been considered by several authors. For example, Sloof \eal \cite{Slooff-2007} introduced a strain-dependent parameter into the initial formulation of the Arrhenius model so that his model could predict the high-temperature flow of a magnesium alloy. Lin \eal \cite{Lin-2008-C}, on the other hand, modified the model by introducing a strain rate compensation factor. Another form of model is developed by Hansel and Spittel \cite{Hensel-1978} whose formulation is based on a product of functions dependent on $\varepsilon$, $\mdot\varepsilon$ and $T$. This model is simple to use and has 8 parameters that are easy to determine. The limitation of this model is its loss of accuracy in some cases when the 8 parameters are defined.
This is why many works often limit its identification to only 5, 6 or 7 parameters.

Most of the developed models are related to a specific material or alloy and where they are used for other materials, their efficiency is not good. To overcome this issue, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model whose formulation can be adapt to any kind of material or alloys. This formulation is based on the MZA model and polynomial functions of undefined order are used during the identification but the problem with this model is the high order of the polynomial function that can affect its accuracy. Therefore a good choice of order of polynomial functions is important during its identification. Another model is that based on artificial intelligence method where parameters identification step of analytical models is replaced by training step.

Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law. It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model. Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited. Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships. Consequently, ANNs have been successfully applied to predict the flow stress behavio of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB, Pantale-2021}.

Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of the model. Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experience correlate well. It is questionable whether a model that correctly describes the behavior of a material can be used to generate data for conditions different from those on which it was identified and how to know the relevance of what it predicts. Interpolation and extrapolation techniques \cite{wahab2017interpolation,luo2019interpolation,stinis2019enforcing} widely used in several fields are extended to the constitutive models in this work where the variable is the strain rate and this can be applied as well as to strain to the temperature. It is a question of choosing a strain rate different from those used during the identification of the model both inside and outside the range of known strain rates. An experiment is therefore carried out for this strain rate in order to validate the prediction of the models. For this purpose, the high-temperature thermomechanical behavior of medium carbon steel alloy subjected to compression tests in a Gleeble thermomechanical simulator was studied. From the experimental data, five analytical models were identified in order to select the one that best describes the behavior of the studied material. A flow model based on an ANN was also developed and identified, and a comparative study between the 5 analytical models and the ANN model is proposed. As presented previously a fundamental concern addressed in this work is the ability of a model to interpolate and extrapolate the results of the model with respect to the range of conditions covered by the experimental tests.

The main parts of this work are as follows: Section \ref{sec:Materials} presents the hardware (Gleeble thermomechanical simulator), the experimental procedure, the material and the results of the compression tests performed for this study.
Section \ref{sec:ConstLaws} is devoted to the presentation of the 5 analytical models, the ANN model, the identification of their parameters and the comparison of the performances of these models with regard to the experimental results.
Section \ref{sec:IntExt} details the interpolation and extrapolation capabilities of each model proposed in this paper.
Conclusions and future work are detailed in Section \ref{sec:Conclusion}.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
\label{fig:RawData}
\end{figure}
All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
So, as we have 6 strain rates and 5 temperatures, the database consists of $21~000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
One reason for the slight increase in stress at low strain rates when the strain is large is due to friction between the sample and the anvil during the test.
For low strain rates, the effect of lubrication decreases over time and thus friction increases.
This results in a progressive increase of the flow stress.

To explain the overall flow stress behavior observed in this test, we will rely on two fundamental phenomena that can be observed during a compression test: Dynamic Recovery (DRV) and Dynamic Recrystallization (DRX).
At the beginning of the deformation of the sample in compression, the amount of dislocations increases and they begin to move within the material, which leads to a rapid increase in stress (strain hardening phenomenon).
As the strain continues to increase, many dislocations are in motion, leading to a stress relaxation phenomenon, generally known as DRV.
This DRV mechanism contributes to the decrease in the number of dislocations due to their combination with another dislocation or due to their integration into a grain boundary.
Some of these dislocations reorganize and then form sub-grains within the initial grains of the material.
The combination of these dislocations moderates the increase in the number of dislocations related to work hardening and thus controls the amount of strain energy stored in the material, which influences the increase in flow stress.
The DRX concerns the germination of new grains, at the borders or inside the initial grains. In addition to the softening phenomena hardening such as deformation induced precipitation and phase transformation that could take place and therefore affect the material behavior. All these phenomena explain the different flow stress curves observed for this alloy.
As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
\label{fig:Micrography}
\end{figure}
As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

%----------------------------------------------------------------------------------
\subsection{Proposed technique for better interpolation}
%----------------------------------------------------------------------------------
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/Performance}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=5~\ps$}
\label{fig:Performance}
\end{figure}
In this part a technique is proposed to have a better interpolation of data. Indeed, as mentioned in the introduction, it is important to know how to reassure oneself of the effectiveness of the model that well describes the behavior of a material for a good use on new data. It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data. The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
\begin{equation}
 \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
\end{equation}
Where $\dot{\varepsilon}_{p}$ is the unkown strain rate and $m\in[50-300]$
Applaying this formule the new figures are plotted in Figure \ref{fig:Performance}. From these results we can see clearly that the results are better that the initial ones. 
\section{Conclusions and future work\label{sec:Conclusion}}
%----------------------------------------------------------------------------------

>>>>

% !TeX encoding = UTF-8
\documentclass[twoside,english,1p,final,sort&compress]{elsarticle}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\pagestyle{headings}
\usepackage{amsthm}
\usepackage{gensymb}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{xcolor}
\usepackage{amssymb}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{placeins}
\usepackage{ulem}
\usepackage[colorlinks = true]{hyperref}

@@

%----------------------------------------------------------------------------------
\section{Introduction\label{sec:Introduction}}
%----------------------------------------------------------------------------------
Large size forged blocks made of medium carbon high-strength steels are extensively used in automotive industry as dies for the production of bumpers and dashboards through the plastic injection process. The manufacturing process of the large blocks starts with ingot casting, followed by open die forging, and quench $\&$ temper heat treatment process to achieve the desired mechanical properties  \cite{chadha2017deformation,chadha2018influence,murugesan2019two}. In recent years, in order to respond to the market demand, larger size forgings need to be produced. In parallel, more stringent condition on chemical homogeneity, hardness, grain size and mechanical properties from the surface to the core of the forged block are required. Among the three manufacturing steps (casting, forging, heat treatment), forging is the one where the most important microstructural changes take place and influences the final properties that could be achieved \cite{murugesan2019hybrid,chadha2020microstructure,sripada2022effect}. Open die forging process is fundamentally a hot compression process during which work strengthening effects, such as hardening (WH) and precipitation, concomitantly take place with softening phenomena such as   recovery and recrystallization under static and/or dynamic \cite{tian2022deformation,tavakoli2019ferrite}. It has also been reported that phase transformation could take place during deformation. The extent and intensity of the above strengthening or softening phenomena strongly depend on three macroscopic quantities \ie the strain $\varepsilon$, the strain rate $\mdot\varepsilon$ and the temperature $T$  \cite{ ebrahimi2017flow,Ashtiani-2012,He-2013, Changizian-2012}.

Considering the large size of the blocks, a purely experimental approach, based on trial and error, could not be used by industry and reliable predictive tools, such a Finite Element analysis (FEA) codes have been developed and are commercially available. However, the prediction reliability of such analyses is dependent on the accuracy of the material constitutive model, which describes the mutual interactions between strain, strain rate, and temperature during deformation. Precipitation and phase changes as mentioned above are considered negligible as deformation takes place in the austenite at temperatures above the dissolution temperature of most carbides. Hence most of the constitutive models depend on macroscopic parameters that influence the hardening and softening of the material. A large number of phenomenological, semi-empirical, or physical models \cite{Rusinek-2010, Shin-2010, Lin-2011, Pantale-2021} have been developed among them, the Johnson-Cook (JC) \cite{Johnson-1983}, Hansel-Spittel (HS) \cite{chadha2018approach}, and Zerilli-Armstrong (ZA) \cite{Zerilli-1987} models are the best known and most widely available in FEA codes. Despite their simplicity, each of them suffer from shortcomings: as reported by Jia \eal \cite{Jia-2021}, the JC model suffers from lack of non-coupling between strain, strain rate and temperature  while the HS model is better adapted for higher strain rate deformation conditions \cite{chadha2018approach}. To circumvent these shortcomings, several modified forms of models have been developed \cite{chadha2018approach, Rule-1998, Vural-2003, Lin-2010, Lin-2012}. However, as reported by many authors \cite{Li-2013, Zhang-2015, Zhou-2019}, even after adjusting the constants, the high temperature flow behavior, particularly when dynamic recrystallization takes place, could not be accurately predicted and none of the models is able to accurately predict flow behavior outside the experimental testing interval that was used to determine the model constants. Due to its more physics-based formulation, the ZA model and its modified form, MZA, \cite{NematNasser-2004, Lennon-2004, Muralli-2017, Cheng-2021, Muralli-2021} and the Arrhenius-type hyperbolic sine constitutive models are preferred to the JC and HS  models both for the prediction of the hot deformation behavior and microstructure analysis of the material \cite{Jonas-1969, Mostafaei-2012, Zhang-2012}. The Arrhenius formulation has been revised several times for a more accurate determination of the activation energy for high temperature deformation \cite{Slooff-2007, Lin-2008-C}. To overcome the strong dependency of the models to a specific alloy, Tize Mha \eal \cite{TizeMha-2022} recently proposed a constitutive model, PTM, whose formulation is independent of the alloy type. This formulation is based on the MZA model and polynomial functions of undefined order that are used during the identification. However, in the PTM model, the high order of the polynomial function (up to $10$ in some cases) can affect its accuracy.

Artificial Neural Network (ANN) is an approach to predict the flow stress behavior of materials without requiring a mathematical formulation of the flow law. It is therefore not necessary to postulate a mathematical expression to identify the parameters of the model. Since the behavior of materials is highly nonlinear at high temperatures, and depends on many factors that are also nonlinear, the evaluation of the flow stress behavior by an analytical model whose parameters are identified by a classical regression method is limited. Faced with these limitations, ANN models are of major interest because they are particularly suited to deal with complex and nonlinear relationships. Consequently, ANNs have been successfully applied to predict the flow stress behavior of materials under hot working conditions \cite{Lin-2008-ANN, Lu-2011-ANN, Ashtiani-2016-CSP, Stoffel-2019-NNB}. Although ANN models can predict well the material flow behavior, there is a problem with its implementation in finite element software as reported by Pantalé \eal \cite{Pantale-2021}. In fact, the implementation of constitutive model in a FEA code requires the derivatives of this model with respect to strain, strain rate and temperature.

Although progress has been made in improvement of constitutive models to better predict the flow stress behavior of materials, there is still a problem with the efficiency of all the above models. Indeed, a model is considered appropriate to the prediction of the material's behavior when its predictions and experimental results correlate well. It is questionable whether a model that correctly describes the behavior of a material in a defined experimental window can be used to accurately predict its behavior for conditions different from those it was identified for. In other words, can interpolation and extrapolation techniques be used to extent the applicability of a constitutive equation for different materials and processing windows?

The present work aims to address the above question using a combination of the recently introduced PTM model and ANN. To this end, initially, hot compression tests, simulating the open die forging process, were carried out and the generated flow curves were modeled using the above mentioned constitutive equations and an ANN model developed in this work. Then the interpolation and extrapolation capabilities of each model is evaluated and a solution is proposed that responds to the main question of the paper. The results are validated based on experimental work carried out in the present work and data obtained from the literature.

@@

The set of flow stress $\sigma^y$ versus strain $\varepsilon$ curves obtained from compression tests performed on the Gleeble-3800 simulator for each test condition (6 strain rates and 5 temperatures) is presented in Figure \ref{fig:RawData}.
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{Figures/rawData}
\caption{Stress-strain curves of medium carbon alloy extracted from the Gleeble device at various temperatures $T$ and strain rates $\mdot\varepsilon$.}
\label{fig:RawData}
\end{figure}
All data curve contains $700$ equidistant strain values up-to $\varepsilon=0.7$.
So, there are $6$ strain rates and $5$ temperatures, the database consists of $21~000$ data points.
The overall behavior of these curves shows that the flow stress $\sigma^y$ increases with increasing strain rate $\mdot\varepsilon$ but decreases with increasing temperature $T$.
It should be noted that the strain also influences the flow stress.
Indeed, for the lowest strain rates $\mdot\varepsilon$, the flow stress $\sigma^y$ increases with the strain $\varepsilon$ until a value of about $\varepsilon=0.2$ to $0.3$, then decreases to maintain a more or less constant value until the end of the test.
For the highest strain rates ($1~\ps$, $2~\ps$, and $5~\ps$), the flow stress increases throughout the test.
The slight increase in stress at low strain rates, when the strain is large, has been reported to be due to friction between the sample and the anvil during the test \cite{buckley2001deformation}. The frictional effect is also visible when testing at low strain rates, as the effect of lubrication decreases over time and thus friction increases. The increase of stresses observed at the beginning of the deformation up to $0.1$ is due to the work hardening (WH). After $0.1$ up to $0.2$ the flow stress shows a continuous reduction with increasing stress until a peak or an inflection of work-hardening rate. This behavior describes that thermal softening becomes more and more predominant until it exceeds WH. At this step, the stress curve shows three different patterns with the increasing strain: (i) gradual decrease to a steady state with DRV/DRX softening. This is the case for all deformation temperatures and strain rates between $0.001$ and $0.1$ \text{s}$^{-1}$ except those at $1050^\circ$C and $1100^\circ$C; (ii) higher stress levels without significant softening and work-hardening at $1050^\circ$C and $1100^\circ$C and strain rate of $0.1$ $\text{s}^{-1}$ ; and (iii) continuous increase with significant work hardening (all deformation temperatures and strain rate of $1$ \text{s}$^{-1}$). Therefore, it can be concluded that the softening due to DRX, characterized by a flow curve with a single peak followed by a steady-state flow, takes place at high temperatures and low strain rates. In contrast, at higher strain rates and lower temperatures, the higher work hardening rate slows down the rate of softening due to DRX, and therefore, both the peak stress and the onset of steady-state flow are shifted to higher strain levels. In fact, the drop observed in
stress is because of DRX occurrence at all temperatures and strain rates of $0.001$–$5$ $\text{s}^{-1}$. As an example, Figure \ref{fig:Micrography} shows the microstructures of medium carbon held during $5$~min at $1260\celsius$ before and after the compression phase.
\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/BeforeCompM}
\caption{Before hot compression}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.45\columnwidth}
\centering
\includegraphics[width=\columnwidth]{Figures/AfterCompM}
\caption{After hot compression}
\end{subfigure}
\caption{Optical micrographs of a medium carbon steel before (a) and after (b) hot compression.}
\label{fig:Micrography}
\end{figure}
As observed on the flow curves reported in Figure \ref{fig:RawData}, it can be seen by comparing the two micrographs in Figure \ref{fig:Micrography} that recrystallization is almost complete for this temperature and strain rate within the sample held for 5 minutes at $1260^\circ$C and rapidly cooled to get autenized grain in one hand and in other hand held for $1$ minute at $1150^\circ$C before compression with strain rate $0.001~\text{s}^{-1}$.
From the results reported in Figure \ref{fig:RawData}, the identification of the parameters of the 6 proposed flow laws will be presented in the next section in order to predict the behavior of the material in any test condition.

@@

%----------------------------------------------------------------------------------
\subsection{Proposed technique for better interpolation}
%----------------------------------------------------------------------------------
\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]
{Figures/Performance}
\caption{Comparison between the experimental (dot) and predicted flow stresses $\sigma^y$ (lines) for $\mdot\varepsilon=1~\ps$}
\label{fig:Performance}
\end{figure}
In this part a technique is proposed to have a better interpolation of data. Indeed, as mentioned in the introduction, it is important to know how to reassure oneself of the effectiveness of the model that well describes the behavior of a material for a good use on new data. It is therefore a question of choosing models that have a good correlation with experience and proposing a formula for a good use of their parameters on unknown data. The AR, HS, PTM and ANN models are therefore chosen and it emerges that each model must be multiplied by a lambda factor whose formula is given as follows.
\begin{equation}
 \lambda = \left(\frac{\dot{\varepsilon}_{max} - \dot{\varepsilon}_{p} }{\dot{\varepsilon}_{p} - \dot{\varepsilon}_{min}}\right)^{\frac{\dot{\varepsilon}_p}{m}}
\end{equation}
Where $\dot{\varepsilon}_{p}$ is the unkown strain rate and $m\in[50-300]$
Applaying this formule the new figures are plotted in Figure \ref{fig:Performance}. From these results we can see clearly that the results are better that the initial ones. 
\section{Conclusions and future work\label{sec:Conclusion}}
%----------------------------------------------------------------------------------
